### 2022-08-31 Bloods Data Sheet.Rmd
created plots for presentation

>>>>

#calculating Percentage Change
##CK
```{r}
CK_PCHANGE <- main_df2%>%
  summarySE(measurevar = "cal_CK", groupvar =c("Session", "Time_Point","Participant"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)

```{r}
write.csv(CK_PCHANGE,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\CK_PCHANGE (29-08-2022).csv",row.names = FALSE)
```

```{r}
CK_PCHANGE_CL <- read.csv("C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Percentage Change\\CK_PCHANGE (29-08-2022).csv")
```

```{r}
CK_PCHANGE_CL<-CK_PCHANGE_CL%>%
  mutate(P_CHANGE = ((CK_POST-CK_PRE)/CK_PRE)*100)

CK_PCHANGET2_SUM <-CK_PCHANGE_CL%>% 
summarySE(measurevar = "P_CHANGE", groupvar =c("Time_Point", "BFR", "Speed", "Session"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)

```{r}
names(main_df2)
```

##LDH
```{r}
LDH_PCHANGE <- main_df2%>%
  summarySE(measurevar = "cal_LDH", groupvar =c("Session", "Time_Point","Participant"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)

```{r}
write.csv(LDH_PCHANGE,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\LDH_PCHANGE (29-08-2022).csv",row.names = FALSE)

LDH_PCHANGE_CL <- read.csv("C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Percentage Change\\LDH_PCHANGE (29-08-2022).csv")
```

```{r}
LDH_PCHANGE_CL<-LDH_PCHANGE_CL%>%
  mutate(P_CHANGE = ((LDH_POST-LDH_PRE)/LDH_PRE)*100)

LDH_PCHANGET2_SUM <-LDH_PCHANGE_CL%>% 
summarySE(measurevar = "P_CHANGE", groupvar =c("Time_Point", "BFR", "Speed", "Session"), na.rm = TRUE, conf.interval = 0.95, .drop = TRUE)

### 2022-08-31 Draft Plots.Rmd
created plots for presentation

Bla_SUM$Speed_f = factor(Bla_SUM$Speed, levels=c("SW", "FW"))
 Speed.labs<- c("Low-Intensity","Moderate-Intensity")
 names(Speed.labs)<-c("SW", "FW")

@@

Bla_PLOT_1 <- ggplot(Bla_SUM, aes(x = Time_Point_f, y= Bla))+
            geom_errorbar(aes(ymin = Bla-se, ymax =Bla+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

@@

            scale_shape_manual(name = "Session_f",
                           labels = Session_f.labs,
                           values = c(22, 15, 21, 16))+
            theme_classic()+
            theme(legend.position="right", legend.title=element_blank())+
            xlab("\n Collection Time Point")+
            scale_y_continuous(name = "Blood Lactate Concentration (mmol/L) \n",breaks = c(0,1,2,3,4,5,6), limits = c(0,6))+
            scale_x_discrete(breaks=c("1", "2", "3"),
              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))

@@

```{r}
ggsave(plot=Bla_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//Blaplot_Draft(25-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)

@@

Na_PLOT_2 <- ggplot(Na_SUM2, aes(x = Time_Point_f, y= cal_Na))+
            geom_errorbar(aes(ymin = cal_Na-se, ymax =cal_Na+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

@@

@@

K_PLOT_2 <- ggplot(K_SUM2, aes(x = Time_Point_f, y= cal_K))+
            geom_errorbar(aes(ymin = cal_K-se, ymax =cal_K+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

@@

@@

Cl_PLOT_2 <- ggplot(Cl_SUM2, aes(x = Time_Point_f, y= cal_Cl))+
            geom_errorbar(aes(ymin = cal_Cl-se, ymax =cal_Cl+se, group = Session), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

@@

@@

>>>>

Bla_SUM$Speed_f = factor(Bla_SUM$Speed, levels=c("SLOW", "FAST"))
 Speed.labs<- c("Low-Intensity","Moderate-Intensity")
 names(Speed.labs)<-c("SLOW", "FAST")

@@

FWBFR_Bla_Finger <- data.frame(Time_Point_f = c("2"),
                         Bla = c(6),
                         Session_f = c("FWBFR"))

FWBFR_Bla_Toe <- data.frame(Time_Point_f = c("3"),
                         Bla = c(6),
                         Session_f = c("FWBFR"))

FW_Bla_Toe <- data.frame(Time_Point_f = c("3"),
                         Bla = c(5),
                         Session_f = c("FW"))

SWBFR_Bla_Finger <- data.frame(Time_Point_f = c("2"),
                         Bla = c(4),
                         Session_f = c("SWBFR"))

SWBFR_Bla_Toe <- data.frame(Time_Point_f = c("3"),
                         Bla = c(4),
                         Session_f = c("SWBFR"))

Bla_PLOT_1 <- ggplot(Bla_SUM, aes(x = Time_Point_f, y= Bla))+
            geom_errorbar(aes(ymin = Bla-se, ymax =Bla+se, group = Session_f), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session_f), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

@@

            scale_shape_manual(name = "Session_f",
                           labels = Session_f.labs,
                           values = c(21, 16,22, 15))+
            theme_classic()+
            theme(legend.position="bottom", legend.title=element_blank())+
            xlab("\n Collection Time Point")+
            scale_y_continuous(name = "Blood Lactate Concentration (mmol/L) \n",breaks = c(0,1,2,3,4,5,6), limits = c(0,6))+
            scale_x_discrete(breaks=c("1", "2", "3"),
              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))+

                  theme(axis.line = element_line(colour = "black", size = 0.4, linetype = "solid"),
                  axis.text.x=element_text(size=16, colour="black"),
                  axis.text.y=element_text(size=16, colour="black"))+
                  theme(axis.text.x=element_text(size=16, angle = 0),
                   axis.title.x=element_text(size=16),
                   axis.title.y=element_text(size=18),
                   strip.text.y=element_text(size=14,face="italic"),
                   strip.text.x=element_text(size=16,face="italic"),
                   legend.title = element_blank())+
                   theme(legend.text=element_text(size=16))+

                  geom_text(size=6,data = FWBFR_Bla_Finger, label = "a #       ")+  
                   geom_text(size=6,data = FWBFR_Bla_Toe, label = "a  #     ")+
                   geom_text(size=6,data = FW_Bla_Toe, label = "a")+
                   geom_text(size=6,data = SWBFR_Bla_Finger, label = "#")+
                   geom_text(size=6,data = SWBFR_Bla_Toe, label = "#")

@@

```{r}
ggsave(plot=Bla_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//Blaplot_Draft(31-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)

@@

Na_PLOT_2 <- ggplot(Na_SUM2, aes(x = Time_Point_f, y= cal_Na))+
            geom_errorbar(aes(ymin = cal_Na-se, ymax =cal_Na+se, group = Session_f), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session_f), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

@@

            scale_shape_manual(name = "Session_f",
                           labels = Session_f.labs,
                           values = c(21, 16, 22, 15))+
            theme_classic()+
            theme(legend.position="", legend.title=element_blank())+
            xlab("\n Collection Time Point")+
            scale_y_continuous(name = "Sodium (mmol/L) \n",breaks = c(100,125,150,175,200), limits = c(100,200))+
            scale_x_discrete(breaks=c("1", "2", "3"),
              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))+

  theme(axis.line = element_line(colour = "black", size = 0.4, linetype = "solid"),
                  axis.text.x=element_text(size=16, colour="black"),
                  axis.text.y=element_text(size=16, colour="black"))+
                  theme(axis.text.x=element_text(size=10, angle = 0),
                   axis.title.x=element_text(size=16),
                   axis.title.y=element_text(size=18),
                   strip.text.y=element_text(size=14,face="italic"),
                   strip.text.x=element_text(size=16,face="italic"),
                   legend.title = element_blank())+
                   theme(legend.text=element_text(size=16))

@@

K_PLOT_2 <- ggplot(K_SUM2, aes(x = Time_Point_f, y= cal_K))+
            geom_errorbar(aes(ymin = cal_K-se, ymax =cal_K+se, group = Session_f), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session_f), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

@@

            scale_shape_manual(name = "Session_f",
                           labels = Session_f.labs,
                           values = c(21, 16, 22, 15))+
            theme_classic()+
            theme(legend.position="", legend.title=element_blank())+
            xlab("\n Collection Time Point")+
            scale_y_continuous(name = "Potassium (mmol/L) \n",breaks = c(4,5,6,7,8,9,10), limits = c(4,10))+
            scale_x_discrete(breaks=c("1", "2", "3"),
              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))+

  theme(axis.line = element_line(colour = "black", size = 0.4, linetype = "solid"),
                  axis.text.x=element_text(size=16, colour="black"),
                  axis.text.y=element_text(size=16, colour="black"))+
                  theme(axis.text.x=element_text(size=10, angle = 0),
                   axis.title.x=element_text(size=16),
                   axis.title.y=element_text(size=18),
                   strip.text.y=element_text(size=14,face="italic"),
                   strip.text.x=element_text(size=16,face="italic"),
                   legend.title = element_blank())+
                   theme(legend.text=element_text(size=16))

@@

Cl_PLOT_2 <- ggplot(Cl_SUM2, aes(x = Time_Point_f, y= cal_Cl))+
            geom_errorbar(aes(ymin = cal_Cl-se, ymax =cal_Cl+se, group = Session_f), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session_f), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

@@

            scale_shape_manual(name = "Session_f",
                           labels = Session_f.labs,
                           values = c(21, 16, 22, 15))+
            theme_classic()+
            theme(legend.position="", legend.title=element_blank())+
            xlab("\n Collection Time Point")+
            scale_y_continuous(name = "Chlorine (mmol/L) \n",breaks = c(50,75,100,125,150), limits = c(50,150))+
            scale_x_discrete(breaks=c("1", "2", "3"),
              labels=c("Pre-Exercise", "Post-Exercise Finger", "Post-Exercise Toe"))+
  theme(axis.line = element_line(colour = "black", size = 0.4, linetype = "solid"),
                  axis.text.x=element_text(size=16, colour="black"),
                  axis.text.y=element_text(size=16, colour="black"))+
                  theme(axis.text.x=element_text(size=10, angle = 0),
                   axis.title.x=element_text(size=16),
                   axis.title.y=element_text(size=18),
                   strip.text.y=element_text(size=14,face="italic"),
                   strip.text.x=element_text(size=16,face="italic"),
                   legend.title = element_blank())+
                   theme(legend.text=element_text(size=16))

@@

#Percentage Change
##CK
CK_PCHANGET2_SUM

```{r}
CK_PCHANGET2_SUM$Session_f = factor(CK_PCHANGET2_SUM$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
 Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
 names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")

#Cl_SUM2$Speed_f = factor(Cl_SUM2$Speed, levels=c("SW", "FW"))
 #Speed.labs<- c("Low-Intensity","Moderate-Intensity")
 #names(Speed.labs)<-c("SW", "FW")

CK_PCHANGET2_SUM$Time_Point_f = factor(CK_PCHANGET2_SUM$Time_Point, levels=c("2", "3"))
Time_Point.labs<- c("Post-Exercise Finger", "Post-Exercise Toe")
names(Time_Point.labs)<-c("2", "3")

CK_PLOT_PCHANGE <- ggplot(CK_PCHANGET2_SUM, aes(x = Time_Point_f, y= P_CHANGE))+
            geom_errorbar(aes(ymin = P_CHANGE-se, ymax =P_CHANGE+se, group = Session_f), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session_f), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

            scale_shape_manual(name = "Session_f",
                           labels = Session_f.labs,
                           values = c(21, 16, 22, 15))+
            theme_classic()+
            ggtitle("Creatine Kinase")+
            theme(plot.title = element_text(hjust = 0.5))+
            theme(legend.position="", legend.title=element_blank())+
            xlab("\n Collection Time Point")+
            scale_y_continuous(name = "Percentage Change \n",breaks = c(-10,0,10,20,30,40,50), limits = c(-10,50))+
            scale_x_discrete(breaks=c("2", "3"),
              labels=c("Post-Exercise Finger", "Post-Exercise Toe"))+

             theme(axis.line = element_line(colour = "black", size = 0.4, linetype = "solid"),
                  axis.text.x=element_text(size=16, colour="black"),
                  axis.text.y=element_text(size=16, colour="black"))+
                  theme(axis.text.x=element_text(size=16, angle = 0),
                   axis.title.x=element_text(size=16),
                   axis.title.y=element_text(size=18),
                   strip.text.y=element_text(size=14,face="italic"),
                   strip.text.x=element_text(size=16,face="italic"),
                   legend.title = element_blank())+
                   theme(legend.text=element_text(size=16))

CK_PLOT_PCHANGE

```
##LDH
```{r}
LDH_PCHANGET2_SUM
```

```{r}
LDH_PCHANGET2_SUM$Session_f = factor(LDH_PCHANGET2_SUM$Session, levels=c("SW","SWBFR","FW", "FWBFR"))
 Session_f.labs<- c("Low-Intensity", "Low-Intensity + BFR", "Moderate-Intensity", "Moderate-Intensity + BFR")
 names(Session_f.labs)<-c("SW","SWBFR","FW", "FWBFR")

#Cl_SUM2$Speed_f = factor(Cl_SUM2$Speed, levels=c("SW", "FW"))
 #Speed.labs<- c("Low-Intensity","Moderate-Intensity")
 #names(Speed.labs)<-c("SW", "FW")

LDH_PCHANGET2_SUM$Time_Point_f = factor(LDH_PCHANGET2_SUM$Time_Point, levels=c("2", "3"))
Time_Point.labs<- c("Post-Exercise Finger", "Post-Exercise Toe")
names(Time_Point.labs)<-c("2", "3")

LDH_PLOT_PCHANGE <- ggplot(LDH_PCHANGET2_SUM, aes(x = Time_Point_f, y= P_CHANGE))+
            geom_errorbar(aes(ymin = P_CHANGE-se, ymax =P_CHANGE+se, group = Session_f), width = 0.3, colour = "black", position = position_dodge(width = 0.5))+
            geom_point(aes(shape = Session_f), fill = "white", colour = "black", size = 5, stroke = 1.8, position = position_dodge(width = 0.5))+

            scale_shape_manual(name = "Session_f",
                           labels = Session_f.labs,
                           values = c(21, 16,22, 15))+
            theme_classic()+
            ggtitle("Lactate Dehydrogenase")+
            theme(plot.title = element_text(hjust = 0.5))+
            theme(legend.position="", legend.title=element_blank())+
            xlab("\n Collection Time Point")+
            scale_y_continuous(name = "Percentage Change \n",breaks = c(-10,0,10,20,30,40,50), limits = c(-10,50))+
            scale_x_discrete(breaks=c("2", "3"),
              labels=c("Post-Exercise Finger", "Post-Exercise Toe"))+

            theme(axis.line = element_line(colour = "black", size = 0.4, linetype = "solid"),
                  axis.text.x=element_text(size=16, colour="black"),
                  axis.text.y=element_text(size=16, colour="black"))+
                  theme(axis.text.x=element_text(size=16, angle = 0),
                   axis.title.x=element_text(size=16),
                   axis.title.y=element_text(size=18),
                   strip.text.y=element_text(size=14,face="italic"),
                   strip.text.x=element_text(size=16,face="italic"),
                   legend.title = element_blank())+
                   theme(legend.text=element_text(size=16))

LDH_PLOT_PCHANGE

```{r}
PCHANGE_Grouping <- ggarrange(CK_PLOT_PCHANGE,LDH_PLOT_PCHANGE,labels=c("A", "B"), ncol=2, nrow=1, common.legend = TRUE, legend = "bottom")

PCHANGE_Grouping
```

```{r}
ggsave(plot=PCHANGE_Grouping,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//PCHANGE_Grouping_Draft(31-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)

##Electrolyte Grouping
```{r}
ELECTROLYTE_Grouping <- ggarrange(Na_PLOT_2,Cl_PLOT_2,K_PLOT_2,labels=c("A", "B", "C"), ncol=3, nrow=1, common.legend = TRUE, legend = "bottom")

ELECTROLYTE_Grouping
```

```{r}
ggsave(plot=ELECTROLYTE_Grouping,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//ELECTROLYTE_Grouping(31-08-2022).png", units = "in",width = 18, height = 8, dpi = 1200)
